### 2022-07-31 papers.tex
Last minute add ad, fixed unicode troubles that was borking lulu
Updated name and email use in front matter, paper, and reference to prior work.

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{TODO: Tell next year's committee that they should probably avoid further milking of the blindsight joke}

@@

\addtrack
    {}{Programming Languages}
\addpaper
    {Modernized Python}
    {Daniel Ng}
    {Keywords:programming languages, type theory, python, sml}
    {SIGBOVIK_2022_paper_0413}
    {0cm}
    {}
\addpaper
    {Grand Challenges in Programming Languages Position Paper: What, if anything, does multiplication even mean?}
    {Jim McCann}
    {multiplication, punctuation: *, punctuation: x, punctuation: ., grand challenges}
    {SIGBOVIK_2022_paper_3280}
    {0cm}
    {}
\addpaper
    {A Type-and-Affect System for Semisignificant Whitespace}
    {Stefan Muller}
    {Keywords: whitespace, white space, white\\nspace}
    {SIGBOVIK_2022_paper_6424}
    {0cm}
    {}

\addpaper
    {brainfuck++: a much needed extension to brainfuck}
    {Cédric Ho Thanh}
    {Keywords: Programing langage, brainfuck, concurrency, machine learning}
    {SIGBOVIK_2022_paper_3995}
    {0cm}
    {\badges{\badge{pagenumbers}}}
%\addreview
%    {SIGBOVIK_2021_review_5}
%    {0cm}

\addtrack
    {}{Other Languages}

\addpaper
    {Tironiculum: Latin Speech Recognition via Latin Text-to-Speech}
    {Lee Butterman}
    {Keywords: Latin, Automatic speech recognition, AI, Machine Learning, Abundant citations, Life advice, State of the Art, Competition winner, Metagaming a competition}
    {SIGBOVIK_2022_paper_0950}
    {0cm}
    {}
\addpaper
    {Abecedarial Acrostic, Alphabetized Amusingly Because Beings Blissfully Cause Celebratory Centennials... (Note: Full Title is Longer)}
    {Jacob Weiner}
    {Keywords: Records, Useless, Alphabet, Gibberish}
    {SIGBOVIK_2022_paper_1598}
    {0cm}
    {}

\addpaper
    {On ``Ra-men, Ra-men ramen ramen''}
    {LAPP Lab}
    {Keywords: language, ramen, space-time continuum}
    {SIGBOVIK_2022_paper_8333}
    {0cm}
    {}

\addpaper
    {ACTION: A Catchy Title Is all yOu Need!}
    {Bernhard Egger, Kevin Smith, Thomas O'Connell and Max Siegel}
    {Keywords: catchy, title, all you need}
    {SIGBOVIK_2022_paper_8346}
    {0cm}
    {}

\addpaper
    {A Deep Learning Approach for Deeply Inaccurate Wordle Solving}
    {Ahana Deb and Sayan Goswami}
    {Keywords: wordle, ordlew, rdlewo, dlewor, leword, ewordl}
    {SIGBOVIK_2022_paper_7404}
    {0cm}
    {}

\addtrack
    {}{Astrophysics}
\addpaper
    {Method and Tool for Estimating the Mass of the Black Hole Located in the Office of Immigration, Refugees and Citizenship Canada Causing a Supermassive Time Dilation in the Visa Extension Process}
    {Étienne Trottoir-Barré, Richard von Pamplemousse and Jessica G. Lasso}
    {Keywords: black hole, abracadabra, hyper driven devices, natural language processing, Chevy Tahoes}
    {SIGBOVIK_2022_paper_0714}
    {0cm}
    {}
\addpaper
    {Black Hole Computation}
    {Matias Scharager}
    {Keywords: monad, computation, compilation, computational trinitarianism, parallel universe, parallel computing}
    {SIGBOVIK_2022_paper_2805}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Schrödinger’s SAT: Generalizing Quantum Bogosort to Prove P = NP Under Many-Worlds Quantum Mechanics}
    {Melody Horn}
    {Keywords: satisfiability, time complexity, revolutions in our understanding of computing, unsolved problems in millennium prize eligibility}
    {SIGBOVIK_2022_paper_6784}
    {0cm}
    {}

\addpaper
    {Solving Double Execution of Java’s paint() Method by Counting Down to the Heat Death of the Universe (plus language compendium)}
    {Braden Oh, Vedaant Kuchhal, Junseok Kang, Andrew Mascillaro, Justin Kunimune, Shashank Swaminathan, Devlin Ih, Elias Gabriel, Audrey Lee, Colin Snow, Hyunkyung Rho, Ben Morris, Solomon Greenberg, Mahima Beltur, Anusha Datar, Jonathan Kelley, Pranavi Boyalakuntla, Xander Hughes, Devyn Oh, Aidan Schmitigal}
    {Keywords: Efficient, Effective, Compendium, Languages, Heat death, Overkill}
    {SIGBOVIK_2022_paper_1777}
    {0cm}
    {}
\addtrack
    {}{Climate Science}

\addpaper
    {Towards Cloud Computing}
    {Alex Xie and Alan Hsu}
    {Keywords: cloud computing, deep learning, machine learning, computer vision, toddlers, kahoot, clout, drip, label smoothing, data science, animals, atmospheric sciences, meteorology}
    {SIGBOVIK_2022_paper_2551}
    {0cm}
    {}
\addpaper
    {Ecological Memory Management: Beyond Garbage Collection}
    {Erik Derohanian, Dann Toliver and Saul Field}
    {Keywords: Garbage Collection, Compost, Memory Management, Organic Computing}
    {SIGBOVIK_2022_paper_2558}
    {0cm}
    {}
\addpaper
    {Infrastructure-as-PowerPoint: A No-Code Approach to Cloud Infrastructure Management}
    {Tobias Pfandzelter}
    {Keywords: cloud computing, powerpoint, slideshow bob}
    {SIGBOVIK_2022_paper_3392}
    {0cm}
    {}

\addpaper
    {On the Possibilities and Challenges of Organic UAV-Assisted MEC}
    {S. Wallow, Cardi Nalle, Robin, P. Cock, and Sky Lark}
    {Keywords:chick-a-dee, caw caw, chirp chirp, hoot hoot}
    {SIGBOVIK_2022_paper_9501}
    {0cm}
    {}
\addtrack
    {}{Aesthetics}

\addpaper
    {Real-Time Foliage Simulation}
    {Emma Liu, Sanjay Salem, Daniel Zeng, Mia Tang, Hesper Yin, George Ralph, Anne He, Max Slater}
    {Keywords: real-time, simulation, graphics, rendering}
    {SIGBOVIK_2022_paper_0683}
    {0cm}
    {}

\addpaper
    {Using deep CNNs to prove that I look better than Tom Cruise and Shah Rukh Khan combined}
    {Sagar Bharadwaj Kalasibail Seetharam}
    {Keywords: CNN, Machine Learning, Image Compression}
    {SIGBOVIK_2022_paper_6854}
    {0cm}
    {}

\addpaper
    {EBMP: Efficient Bitmap Encodings on Ethereum Virtual Machines}
    {0XMOSTIMA, Yunsong Liu and Peiyuan Liao}
    {Keywords: still image coding, blockchain, smart contracts, non fungible tokens}
    {SIGBOVIK_2022_paper_5649}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {A Machine Learning Approach To Classifying Cuteness}
    {Anoushka Shrivastava}
    {Keywords: machine learning, classification, cuteness}
    {SIGBOVIK_2022_paper_9240}
    {0cm}
    {}

\addpaper
    {Attractiveness Learning: A General Solution for the Cold-Start Problem}
    {Yajuan Gu and Yuxun Lu}
    {neural network, attractive mechanism, recommender system, cold-start problem}
    {SIGBOVIK_2022_paper_2018}
    {0cm}
    {}

\addtrack
    {}{Best Practices}
%\addpaper
%    {Investigations and Difficulties in Real - to -Sim}
%    {Sashank Tirumala}
%    {Keywords: Robotics, Machine Learning, Deep Learning, Reinforcement Learning}
%    {SIGBOVIK_2022_paper_3472}
%    {0cm}
%    {}
\addpaper
    {Quadruple-Blind Peer Review}
    {Yuriko Shu}
    {Keywords: Peer Review, Quadruple Blind Reviewing, Bias Reduction}
    {SIGBOVIK_2022_paper_3958}
    {0cm}
    {}
\addpaper
    {Optimal degeneracy through OwO based variable names}
    {Fwans Skawman}
    {Keywords: OwO, What's, This}
    {SIGBOVIK_2022_paper_4751}
    {0cm}
    {}

\addpaper
    {Multiplication by repeated addition, with fraction handling.}
    {Jim McCann}
    {Keywords: multiplication, punctuation: *, C++, source code}
    {SIGBOVIK_2022_paper_1824}
    {0cm}
    {}
\addpaper
    {Objective Correlation Metrics for Quality of Code Estimation}
    {Eleftheria Chatziargyriou and Konstantinos Kanavouras}
    {Keywords: programming, quality, code, objective}
    {SIGBOVIK_2022_paper_1957}
    {0cm}
    {}

\addpaper
    {(Un)helper functions}
    {Kevin Smith and Bernhard Egger}
    {Keywords: algorithms, algorithm patent trolling, cite us please!}
    {SIGBOVIK_2022_paper_2133}
    {0cm}
    {}

\addtrack
    {}{Mathematics}

\addpaper
    {Improved Data and Instruction Locality in Long Division}
    {Isaac Grosof, Isaac Grosof}
    {Keywords: performance, division, locality, data, instruction}
    {SIGBOVIK_2022_paper_0463}
    {0cm}
    {}

\addpaper
    {The New New Math: using sentiment analysis of mathematics word problems to gauge children's reactions to teaching 8-bit floating point arithmetic for the new California public school math curriculum}
    {Lee Butterman}
    {Keywords: education, early childhood education, won't someone think of the children, won't someone think of the chiiiiiiildren, new math, California math education guidelines, data science, calculus, graphics processing units, dozens of petaflops, sentiment analysis, numerology, fear of Arabic numerals, 8-bit floating point}
    {SIGBOVIK_2022_paper_4483}
    {0cm}
    {}

\addpaper
    {Infix Modifiers for Flexible Multiplication}
    {Jim McCann}
    {Keywords: multiplication, punctuation: *, infix, IMMs}
    {SIGBOVIK_2022_paper_4549}
    {0cm}
    {}

\addtrack
    {}{Hardware}

\addpaper
    {Correct-It-Yourself Paper Updater}
    {Thomas Chick}
    {Keywords: corrections, arts and crafts, reader participation, sacrilege? sure}
    {SIGBOVIK_2022_paper_4967}
    {0cm}
    {}

\addpaper
    {Harder Drive: Hard drives we didn't want or need}
    {Tom Murphy}
    {Keywords: hard drive, block device, ipv4, tetris, covid-19, chainsaws}
    {SIGBOVIK_2022_paper_4275}
    {0cm}
    {}
\addpaper
    {Just a Regular Paper}
    {Jason Wang}
    {Keywords: Money, Finance, Banking, Social Issues, Machine Learning, Ohio}
    {SIGBOVIK_2022_paper_2759}
    {0cm}
    {}

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {}
\addpaper
    {SEGA-NVidia 32esque Advertisements}
    {Jim McCann}
    {Keywords: sega, nvidia, 3D 3D, rtesque}
    {SIGBOVIK_2022_paper_6593}
    {0cm}
    {}

\addtrack{}{A Brief Musical Interlude}
%\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    {Baby Sharks are More than Sharks . They are Earworms Sung More than Happy Birthday Perhaps}
    {Kofi Oduro}
    {Keywords: Sharks, Happy Birthday, Swimming Shark Problem, Shark Week, billions, humans, kindergarten, PRe-K}
    {SIGBOVIK_2022_paper_6744}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

\addpaper
    {Everybody Clap Your Hands: The Cha Cha Slide is Turing Complete}
    {Harrison Goldstein}
    {Keywords: Turing complete, Cha Cha Slide, line dance, party, complexity}
    {SIGBOVIK_2022_paper_5708}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Exhaustive Survey of Rickrolling in Academic Literature}
    {Benoit Baudry and Martin Monperrus}
    {Keywords: Rickrolling, Academia, Rick Astley}
    {SIGBOVIK_2022_paper_8755}
    {0cm}
    {}

\addtrack
    {}{Construction}

%\addpaper
%    {AI is a Really, Really, Really Bad Idea}
%    {Molly de Blanc}
%    {Keywords: artificial intelligence, ethics, machine learning}
%    {SIGBOVIK_2021_paper_10}
%    {0cm}
%    {}
\addpaper
    {Destructive Logic}
    {Runming Li}
    {Keywords: logic, constructive logic, destructive logic, type theory}
    {SIGBOVIK_2022_paper_6801}
    {0cm}
    {}

\addpaper
    {On Ruinment: Ruination Theory and its Consequents}
    {Luna Tascheter}
    {Ruination Theory, Ruinment, T0T4L PWN4G∃, Category Theory, Adam Conover, Adam Sandler, Hallmark, Waste of Paper, Orange}
    {SIGBOVIK_2022_paper_6808}
    {0cm}
    {}
\addtrack
    {}{Spoops}

\addpaper
    {When Pull Comes To Shove... Do Both!}
    {Ullas A}
    {Keywords: Parallel Programming, Graphs, Connected Components, GPUs}
    {SIGBOVIK_2022_paper_8597}
    {0cm}
    {}

\addpaper
    {man exorcism}
    {}
%    {Akiva Leffert}
    {Keywords:exorcisms, unix, demonology}
    {SIGBOVIK_2022_paper_9978}
    {0cm}
    {}

\addpaper
    {2x a fake submission}
    {Tim Toady}
    {Keywords: one letter keywords are not accepted: f, 21 is not a correct keyword: it contains no letters, =42 is not a correct keyword: it contains no letters}
    {SIGBOVIK_2022_paper_8085}
    {0cm}
    {}

\addpaper
    {A 23 MW data centre is all you need}
    {Samuel Albanie, Dylan Campbell and João Henriques}
    {Keywords: machine learning, prophecy, Molly}
    {SIGBOVIK_2022_paper_4719}
    {0cm}
    {}

\addtrack
    {}{Uhhhh etcetera}

\addpaper
    {Neo-classical Logic: Une Logique non classique}
    {Martin Vassor and Fangyi Zhou}
    {Keywords: Logic, Meta-Metatheory, Law of Excluded Middle, Law of Contradiction, Decidability, Macron}
    {SIGBOVIK_2022_paper_2522}
    {0cm}
    {}

\addpaper
    {A Patriotic Analysis of Programming Paradigms}
    {Jacob Weiner}
    {Keywords: Patriotism, Constitution, Dependent Type Theory}
    {SIGBOVIK_2022_paper_1689}
    {0cm}
    {}

\addpaper
    {A sometimes-accurate O(1) search algorithm}
    {A College Freshman}
    {Keywords:fast, search, search algorithm, searching algorithm, searching, how many ways can i say search algorithm}
    {SIGBOVIK_2022_paper_4297}
    {0cm}
    {}

\addpaper
    {Edward, edMUnD & Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}

\addpaper
    {A Third Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
    {Shalin Shah}
    {Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort}
    {SIGBOVIK_2022_paper_5584}
    {0cm}
    {}
\addpaper
    {this is not a review}
    {Huilian Sophie Qiu}
    {Keywords: this, is, not, review}
    {SIGBOVIK_2022_paper_9376}
    {0cm}
    {}

\addpaper
    {Functorial wrappers for high-dimensional classification algorithms}
    {James Carzon}
    {Keywords: forgetful functor, classification, high dimensional data}
    {SIGBOVIK_2022_paper_7603}
    {0cm}
    {}
\addpaper
    {Overlap-Maximal Graph Labelings: Graph Labelings with Non-Disjoint Vertex and Edge Sets (and how they can be used for encryption, poetry, and breaking mathematics)}
    {Gabriel Chuang}
    {Keywords: Graph Theory, Cryptography, Fox in Socks by Dr. Seuss}
    {SIGBOVIK_2022_paper_6809}
    {0cm}
    {}
\addpaper
    {Analysis of A New Error Calculation Technique}
    {Jevin Tong} 
    {Keywords: late, erroneous, hackneyed}
    {SIGBOVIK_2022_paper_7011}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {}

\addpaper
    {A Free Computer Vision Lesson for Car Manufacturers or It is Time to Retire the Erlkönig}
    {Maximilian Weiherer and Bernhard Egger}
    {Keywords: awesome paper, great work, mind blowing results}
    {SIGBOVIK_2022_paper_9466}
    {0cm}
    {}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Blindsight is also 2021}

@@

\addtrack
    {}{Fun(?) and Games Track}
\addpaper
    {Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
    {Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}
    {Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}
    {SIGBOVIK_2021_paper_5}
    {0cm}
    {\badges{\badge{unusable}}}
\addpaper
    {Demystifying the Mortal Kombat Song}
    {J Devi and Chai-Tea Latte}
    {Keywords: mortal-kombat, truth, meaning-of-life}
    {SIGBOVIK_2021_paper_12}
    {0cm}
    {}
\addpaper
    {Unicode Magic Tricks}
    {Nicolas Hurtubise}
    {Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}
    {SIGBOVIK_2021_paper_13}
    {0cm}
    {}
\addpaper
    {Video games in Fonts Fontemon}
    {Michael Mulet}
    {Keywords: font, video game, font video game, silly idea done seriously}
    {SIGBOVIK_2021_paper_18}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_5}
    {0cm}

\addpaper
    {Soliterrible}
    {Sam Stern}
    {Keywords: solitaire, klondike, cards}
    {SIGBOVIK_2021_paper_27}
    {0cm}
    {\badges{\badge{javascript}}}
\addpaper
    {Opening Moves in 1830: Strategy in Resolving the N-way Prisoner’s Dilemma}
    {Philihp Busby and Daniel Ribeiro E Sousa}
    {Keywords: boardgame, opening, strategy, deterministic, auction}
    {SIGBOVIK_2021_paper_44}
    {0cm}
    {}

\addtrack
    {}{Obligatory Machine Learning Track}
\addpaper
    {Universal Insights with Multi-layered Embeddings}
    {Prophet \#1, Prophet \#2 and Prophet \#3}
    {Keywords: Machine learning, embedding, auto-encoders, Zalgo he comes, dimensional reduction}
    {SIGBOVIK_2021_paper_8}
    {0cm}
    {}
\addpaper
    {Solving reCAPTCHA v2 Using Deep Learning}
    {David Krajewski and Eugene Li}
    {Keywords: deep learning, recaptcha, automation, david}
    {SIGBOVIK_2021_paper_16}
    {0cm}
    {}
\addpaper
    {Deep Deterministic Policy Gradient Boosted Decision Trees}
    {Clayton W. Thorrez}
    {Keywords: machine learning, reinforcement learning, gradient, do these appear anywhere?, ``yes they do'': the proceedings chair}
    {SIGBOVIK_2021_paper_17}
    {0cm}
    {}
\addpaper
    {Tensorflow for Abacus Processing Units}
    {Robert McCraith}
    {Keywords: machine learning, tensor flow, abacus, mathematics, calculus, differentiation, computation}
    {SIGBOVIK_2021_paper_35}
    {0cm}
    {}

\addpaper
    {RadicAI: A Radical, Though Not Entirely New, Approach to AI Paper Naming}
    {Jim McCann and Mike McCann}
    {Keywords: lottery, random, language models}
    {SIGBOVIK_2021_paper_38}
    {0cm}
    {}

\addtrack
    {}{Followup Track}
\addpaper
    {A Note on ``The Consent Hierarchy''}
    {}
    {Keywords: freely given, reversible, informed, enthusiastic, specific}
    {SIGBOVIK_2021_paper_25}
    {0cm}
    {}

\addpaper
    {Another Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
    {Shalin Shah}
    {Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort, Subpar-Quality}
    {SIGBOVIK_2021_paper_28}
    {0cm}
    {}

\addpaper
    {Story Time}
    {Jim McCann and Mike McCann}
    {Keywords: story time, time for stories, the time of stories, stories? it's time, our time is now our time is stories, big data? I get it.}
    {SIGBOVIK_2021_paper_39}
    {0cm}
    {}

\addtrack
    {}{``Type'' Track}
\addpaper
    {Stop Doing Type Theory}
    {}
    {Keywords: Ranting, Raving, Muttering, Grumbling}
    {SIGBOVIK_2021_paper_2}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_3}
    {0cm}
\addpaper
    {If It Type-checks, It Works: FoolProof Types As Specifications}
    {Brandon Wu}
    {Keywords: PL, languages, types, specifications, correctness, type-checking, functional programming}
    {SIGBOVIK_2021_paper_40}
    {0cm}
    {}
\addpaper
    {Oracle Types}
    {Akiva Leffert and Jason Reed}
    {Keywords: types, databases, constraints, texting, machine translation, typescript}
    {SIGBOVIK_2021_paper_21}
    {0cm}
    {\badges{\badge{unavailable}}}
\addpaper
    {Lowestcase and uppestcase letters: Advances in derp learning}
    {Tom Murphy VII}
    {case analysis, derp learning, 3d manifold, chess, exponentiation, fonts}
    {SIGBOVIK_2021_paper_26}
    {0cm}
    {}
\addpaper
    {Dependent Stringly-Typed Programming}
    {gallais}
    {Keywords: dependent stringly typed programming, best practices, agda}
    {SIGBOVIK_2021_paper_34}
    {0cm}
    {\badges{\badge{literate}}}
\addpaper
    {Yet Another Lottery Ticket Hypothesis}
    {Aman Madaan and Gary Yao}
    {Keywords: lottery, random, language models}
    {SIGBOVIK_2021_paper_24}
    {0cm}
    {}

\addtrack
    {}{(Psycho)metrics Track}
\addpaper
    {Spacecraft Attitude Determination and Control}
    {Freddie Rawlins}
    {Keywords: attitude, determination, happy satellites}
    {SIGBOVIK_2021_paper_29}
    {0cm}
    {}

\addpaper
    {Instruction Programs}
    {Jim McCann}
    {Keywords: yoko ono, instruction programs, art jokes, one page papers}
    {SIGBOVIK_2021_paper_22}
    {0cm}
    {}

\addpaper
    {Winning the Rankings Game: A New, Wonderful, Truly Superior CS Ranking}
    {Diogenes}
    {Keywords: CSRankings, computer science rankings, bad proxies for quality, research quality, ego stroking, navel gazing, ranking algorithms}
    {SIGBOVIK_2021_paper_15}
    {0cm}
    {}

\addpaper
    {openCHEAT: Computationally Helped Error bar Approximation Tool - Kickstarting Science 4.0}
    {Bernhard Egger, Kevin Smith and Max Siegel} %TODO: put in crossed out David Cox?
    {Keywords: best, paper, award}
    {SIGBOVIK_2021_paper_9}
    {0cm}
    {}

\addreview
    {SIGBOVIK_2021_review_1}
    {0cm}

\addpaper
    {On the dire importance of MRU caches for human survival (against Skynet)}
    {Darío de la Fuente García, Félix Áxel Gimeno Gil, Juan Carlos Morales Vega and Borja Rodríguez Gálvez}
    {Keywords: Skynet, MS paint, cache, MRU, dMRU, sMRU, NEP}
    {SIGBOVIK_2021_paper_33}
    {0cm}
    {}

\addtrack
    {}{Not Really Biology But Closer to it Than the Other Papers Track}
\addpaper
    {Revenge of the pith: Surveying the landscape of plant-powered scientific literature}
    {Vinay Uday Prabhu}
    {Keywords: Plant powered science, AI, Scientific method, Survey}
    {SIGBOVIK_2021_paper_11}
    {0cm}
    {}

\addreview
    {SIGBOVIK_2021_review_4}
    {0cm}

\addpaper
    {On the Origin of Species of Self-Supervised Learning}
    {Samuel Albanie, Erika Lu and João Henriques}
    {Keywords: self-supervised learning, origin of species, artificial naturalism}
    {SIGBOVIK_2021_paper_43}
    {0cm}
    {}
\addpaper
    {Critical Investigations on Avians: Surveillance, Computational Amorosities, and Machines}
    {Rose Bohrer and Connie Chau}
    {Keywords: Birds, Not, Real}
    {SIGBOVIK_2021_paper_36}
    {0cm}
    {}

\addpaper
    {The Urinal Packing Problem in Higher Dimensions}
    {Shane Guan, Blair Chen, Skanda Kaashyap}
    {Keywords: PvsNP, Max\_Independent\_Set, TCS, Algorithms}
    {SIGBOVIK_2021_paper_6}
    {0cm}
    {}

\addtrack
    {}{ApPLied Theory}
\addpaper
    {The Newcomb-Benford Law, Applied to Binary Data: An Empirical and Theoretic Analysis}
    {Gabriel Chuang and Brandon Wu}
    {Keywords: Numerical Methods, Verification, Poor Proof Style, Statistics}
    {SIGBOVIK_2021_paper_41}
    {0cm}
    {}
\addpaper
    {How to get to second base and beyond - a constructive guide for mathematicians}
    {Raluca Jalaboi and Mads Eiler Hansen}
    {Keywords: damn, forgot, again, deadlines}
    {SIGBOVIK_2021_paper_7}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {NetPlop: A moderately-featured presentation editor built in NetLogo}
    {Patrick Steinmann}
    {Keywords: agent-based slideshows, slide-based models, singularity}
    {SIGBOVIK_2021_paper_37}
    {0cm}
    {\badges{\badge{netlogo}}}

\addtrack{}{(Meta)physics}
\addpaper
    {A Complete Survey of 0-Dimensional Computer Graphics}
    {Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Po Po}
    {Keywords: Computer Graphics, Geometry, Rendering, Animation}
    {SIGBOVIK_2021_paper_30}
    {0cm}
    {}
\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    [fancypyramid]
    {Macro-driven metalanguage for writing Pyramid Scheme programs}
    {Marcin Konowalczyk}
    {Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
    {SIGBOVIK_2021_paper_31}
    {0cm}
    {\badges{\badge{mlm}}}
\addpaper
    {On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
    {Zikuan Wang}
    {Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
    {SIGBOVIK_2021_paper_32}
    {0cm}
    {}
\addpaper
    {Inverted Code Theory: Manipulating Program Entropy}
    {usH nalA dna eiX xelA}
    {Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}
    {SIGBOVIK_2021_paper_23}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

\addtrack
    {}{Definitely Finite Track}

%\addpaper
%    {AI is a Really, Really, Really Bad Idea}
%    {Molly de Blanc}
%    {Keywords: artificial intelligence, ethics, machine learning}
%    {SIGBOVIK_2021_paper_10}
%    {0cm}
%    {}

\addpaper
    {Stone Tools as Palaeolithic Central Unit Processors}
    {}
    {Keywords: recursion, stone tools, computer science, handaxe, processor, prehistory, palaeogaming, psychedelic pragmatism}
    {SIGBOVIK_2021_paper_14}
    {0cm}
    {}

\addpaper
    {Build your own 8-bit busy beaver on a breadboard!}
    {Robert J. Simmons}
    {Keywords: busy beaver, computability, turing machines, algorithms, breadboards, TTL, MacBook Pro}
    {SIGBOVIK_2021_paper_19}
    {0cm}
    {}

\addpaper
    {What Lothar Collatz Thinks of the CMU Computer Science Curriculum}
    {Gabriel Chuang and Brandon Wu}
    {Pedagogy, Precognition, Theoretical Computer Science, Coincidences, Sequences, Category Theory, Computability}
    {SIGBOVIK_2021_paper_42}
    {0cm}
    {}

\addtrack
    {}{Recursive Track}
\addpaper
    {On Sigbovik Paper Maximization}
    {Josh Abrams}
    {Keywords: Maximization, Information Theory, Complexity, Divine Intervention, Academic Integrity, Big Small, Does Anybody Read These Things?, ``I Do'': The Proceedings Chair}
    {SIGBOVIK_2021_paper_20}
    {0cm}
    {}

\addpaper
    {SIGBOVIK 2021 isn't named SIGCOVID}
    {Cameron Wong}
    {Keywords: covid, bovik, short}
    {SIGBOVIK_2021_paper_4}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
    {Nicolas Hurtubise} %TODO: those other authors???
    {Keywords: component, formatting, style, styling, insert}
    {SIGBOVIK_2021_paper_1}
    {0cm}
    {}

\addpaper
    {``The SIGBOVIK paper to end all SIGBOVIK papers'' will not be appearing at this conference}
    {Thomas Chick}
    {Keywords: SIGBOVIK, Statistics, Finality}
    {SIGBOVIK_2021_paper_3}
    {0cm}
    {}
